\documentclass[a4paper, 11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{verbatim}
\usepackage{moreverb}
\usepackage[english]{babel}
%\usepackage{english}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{listings} 
\usepackage{lastpage}
\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}
\usepackage{color}
\usepackage{xcolor}
%font change
\renewcommand{\familydefault}{\sfdefault}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\nl}{\\[0.1cm]}
\newcommand{\s}{\vspace{0.3cm}}
\newcommand{\smore}{\vspace{0.6cm}}

\usepackage{caption}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}

\lstset{frame=single}

\lstdefinelanguage{popc}{%
   morekeywords={%
   %od
      od, url, power, @, 100, 80, machine, POPString, search
  },
  sensitive=true,
  morestring=[b]',
}

\addto\captionsenglish{%
  \renewcommand{\listfigurename}{}%
	\renewcommand\refname{}
}



%Header and footer 
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}

%Header definition
\renewcommand{\headrulewidth}{0.5pt}
\lhead{ViSaG : Virtual Safe GRID}
\rhead{POP-C++ over SSH Tunnel}

%Footer definition
\renewcommand{\footrulewidth}{0.5pt}
\cfoot{\today}
\lfoot{Clément Valentin}
\rfoot{Page \thepage ~on \pageref{LastPage}}

%remove indent for paragraph
\parindent0ex 

%\setlength{\parskip2ex}








%\pagebreak



\begin{document}

\input{title}
%\newpage \thispagestyle{empty} \mbox{}\newpage



\tableofcontents
\pagebreak
\section{Introduction}
ViSaG is a project to enhance the security in a computing grid infrastructure. Under this project, the EIA-FR is in charge of the security implementation in the middle-ware POP-C++. This document explains the different mechanisms to implement inside POP-C++ to use a secure connection over SSH. This document is structured as follows : 
\begin{itemize}
\item The following chapter aims to explain why we choose the SSH tunnelling to implement a secured version of POP-C++.
\item The third chapter presents some alternatives to the SSH tunnelling.
\item The fourth chapter explains the principles of the SSH tunnelling.
\item The fifth chapter is a review of the current situation in POP-C++.
\item The sixth chapter explains the key exchange process choose for POP-C++.
\item The seventh chapter describes all the modifications made to POP-C++ to be able to use the SSH tunnelling.
\item The eighth chapter gives some future possible improvements. 
\item The ninth chapter gives to the end user the major changes that comes with the new version of POP-C++.
\item The tenth chapter is a review of two test scenarios. 
\item The eleventh chapter describes the current known issues. 
\item The last chapter concludes this report. 
\end{itemize}


\input{ssh_tunnelling}
\input{situation}
\input{key_ex}
\pagebreak
\input{implementation}


\pagebreak





\section{Table of figures}
\listoffigures{}

\section{References}
\begin{thebibliography}{9}

\bibitem{ssh}
	IETF,
  	\emph{SSH : Secure Shell (rfc 4251)}.
	Network Working Group, http://www.ietf.org/rfc/rfc4251.txt
	January 2006.
	
\bibitem{vpopc_clement}
	Valentin Clément,
  	\emph{Virtual POP-C++ : road to ViSaG}. GRID and Cloud Computing Group, EIA-FR, Switzerland, November 2010.
  	
\bibitem{valgrind}
	Valgrind Developers,
  	\emph{Valgrind}. http://valgrind.org

\end{thebibliography}


\end{document}
