\documentclass[a4paper, 11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{verbatim}
\usepackage{moreverb}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{listings} 
\usepackage{lastpage}
\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}
\usepackage{color}
\usepackage{xcolor}

%font change
\renewcommand{\familydefault}{\sfdefault}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\nl}{\\[0.1cm]}
\newcommand{\s}{\vspace{0.3cm}}
\newcommand{\smore}{\vspace{0.6cm}}

\usepackage{caption}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}

\lstset{frame=single}

\lstdefinelanguage{popc}{%
   morekeywords={%
   %od
      od, url, power, @, 100, 80, machine, POPString, search
  },
  sensitive=true,
  morestring=[b]',
}

\addto\captionsenglish{%
  \renewcommand{\listfigurename}{}%
	\renewcommand\refname{}
}



%Header and footer 
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}

%Header definition
\renewcommand{\headrulewidth}{0.5pt}
\lhead{ViSaG : Virtual Safe GRID}
\rhead{Version 1.5}

%Footer definition
\renewcommand{\footrulewidth}{0.5pt}
\cfoot{\today}
\lfoot{Valentin Clément}
\rfoot{Page \thepage ~on \pageref{LastPage}}

%remove indent for paragraph
\parindent0ex 

%\setlength{\parskip2ex}








%\pagebreak



\begin{document}

\input{title}
%\newpage \thispagestyle{empty} \mbox{}\newpage



\tableofcontents
\pagebreak
\section{Introduction}
Virtual - POP-C++ is a version of the POP-C++ middle-ware that would be able to run parallel objects into virtual machines. The development of this version is the core of the ViSaG project. A prototype version of Virtual - POP-C++ has been developed during a bachelor thesis project in the summer 2010. This version is called VirtualPOPC-1\cite{vpopc1}.\s

\textit{NOTE : } VirtualPOPC-1 will be referred as VPOP1 in the rest of this document.\s

This document is structured as follows:
\begin{itemize}
\item The next chapter is focusing on the weaknesses of the prototype developed during a Bachelor Thesis. 
\item The Chapter \ref{sec:repartition} aims to dispatch the work between the partner institutions working on this project. 
\item The Chapter \ref{sec:open_points} was written to helps the project team to take the right decisions concerning the future development on this project. 
\item Chapter \ref{sec:modif} explains all the modifications done on the first prototype to make the final version of POP-C++ for ViSaG.
\item Chapter \ref{sec:gen_mod} just explains small modifications that are general to all POP-C++ versions.
\item Chapter \ref{sec:security} tells what we think about the security of our new version.
\item Chapter \ref{sec:test} focuses on functional and performance tests. 
\item Chapter \ref{sec:future} gives some ideas for future development. 

\end{itemize}

Keep in mind this document has been updated during the whole development process. The firsts chapters have been written before the actual development of the new versions. 



\input{weakness}

\pagebreak
\input{hints}

\pagebreak
\input{modifications}

% Securty assumptions
\pagebreak
\input{security}

% Functionality and performance tests
\pagebreak
\input{performance}

% Future development ideas
\pagebreak
\input{future}

\pagebreak
\input{glossary}


\pagebreak
\section{Table of figures}
\listoffigures{}





%
% REFERENCES
%

\section{References}
\begin{thebibliography}{9}
\bibitem{vpopc1}
	Adrian Wyssen,
  	\emph{VirtualPOPC-1 : Project Report}.
	EIA-FR, Switzerland, 
	June-August 2010.
	
\bibitem{popcssh}
	Valentin Clément,
	\emph{POP-C++ over SSH Tunnel}.
	EIA-FR, Fribourg, Switzerland,
	September-November 2010.
	
\bibitem{popc_vs_addon_manual}
	Valentin Clément,
	\emph{POP-C++ Virtual-Secure : POP-C++ User and Installation manual add-on}.
	EIA-FR, Fribourg, Switzerland, 
	January 2011.

\end{thebibliography}


\end{document}
